### 2024-12-15 draft.tex
Added new informal proof without introducing Y

\subsection{The proof of Central Limit Theorem}
\subsubsection{Informal Proof}
Informal proof of Lyapounov's theorem for a single sequence by the method of Lindeberg \cite{chung2000course}.
\begin{itemize}
    \item \textbf{Notation and Statement}
    \begin{enumerate}
    \item \( \{X_j\}_{j=1}^n \) be a sequence of independent random variables with:
    \begin{itemize}
        \item[] \( \mathbb{E}[X_j] = 0 \), 
        \item[] \( \text{Var}(X_j) = \sigma_j^2 \) (finite variances, \( \sigma_j^2 < \infty \)),
        \item[] \( \mathbb{E}[|X_j|^3] = \gamma_j \) (finite third moments, \( \gamma_j < \infty \)).
    \end{itemize}

>>>>

\newpage
\subsection{The proof of Central Limit Theorem}
\subsubsection{Informal Proof without introducing Y ((the replacement Gaussian random variables))}
\begin{itemize}
        \item[] \( \mathbb{E}[X_j] = 0 \), 
        \item[] \( \text{Var}(X_j) = \sigma_j^2 \) (finite variances, \( \sigma_j^2 < \infty \)),
        \item[] \( \mathbb{E}[|X_j|^3] = \gamma_j \) (finite third moments, \( \gamma_j < \infty \)).
    \end{itemize}

Define:
        \begin{itemize}
            \item[] \( S_n = \sum_{j=1}^n X_j \),
            \item[] \( s_n^2 = \sum_{j=1}^n \sigma_j^2 \) (total variance),
            \item[] \( \Gamma_n = \sum_{j=1}^n \gamma_j \) (total third moment).
\end{itemize}

Statement:

    If 
    \[
   \frac{\Gamma_n}{s_n^3} \to 0 \quad \text{as } n \to \infty.
   \]
   then 
   \[
   \frac{S_n}{s_n} \xrightarrow{d} \Phi
   \]
   where \( \Phi\) denotes the standard normal distribution \( \mathcal{N}(0,1) \).

Let $\boldsymbol{Z_n = S_n / s_n }$, to prove $\boldsymbol{Z_n \xrightarrow{d} \mathcal{N}(0,1)}$, it suffices to show that for any bounded, continuous test function \( f \in C_b^3(\mathbb{R}) \) (bounded continuous functions with three bounded derivatives):
\[
\mathbb{E}[f(Z_n)] \to \mathbb{E}[f(\mathcal{N})],
\]

Using Taylor’s theorem, we expand \( f(Z_n) \) around \( 0 \):
\[
f(Z_n) = f(0) + f'(0)Z_n + \frac{f''(0)}{2}Z_n^2 + R(Z_n),
\]
where \( R(Z_n) \) is the remainder:
\[
R(Z_n) = \frac{f^{(3)}(\xi)}{6}Z_n^3,
\]
for some \( \xi \) between \( 0 \) and \( Z_n \).

Taking expectations:
\[
\mathbb{E}[f(Z_n)] = f(0) + f'(0)\mathbb{E}[Z_n] + \frac{f''(0)}{2}\mathbb{E}[Z_n^2] + \mathbb{E}[R(Z_n)].
\]

Similarly, for \( \mathcal{N}(0,1) \), we expand \( f(\mathcal{N}) \):
\[
\mathbb{E}[f(\mathcal{N})] = f(0) + f'(0)\mathbb{E}[\mathcal{N}] + \frac{f''(0)}{2}\mathbb{E}[\mathcal{N}^2] + \mathbb{E}[R(\mathcal{N})].
\]

Thus, the difference becomes:
\[
\mathbb{E}[f(Z_n)] - \mathbb{E}[f(\mathcal{N})] = \underbrace{f'(0) (\mathbb{E}[Z_n] - \mathbb{E}[\mathcal{N}])}_{(a)} + \underbrace{\frac{f''(0)}{2} (\mathbb{E}[Z_n^2] - \mathbb{E}[\mathcal{N}^2])}_{(b)} + \underbrace{(\mathbb{E}[R(Z_n)] - \mathbb{E}[R(\mathcal{N})])}_{(c)}.
\]

By analyzing each term, we have:

\textbf{(a)} $\boldsymbol{f'(0) (\mathbb{E}[Z_n] - \mathbb{E}[\mathcal{N}])}$
\begin{itemize}
    \item By assumption, \( \mathbb{E}[X_j] = 0 \), so \( \mathbb{E}[S_n] = 0 \), and:
  \[
  \mathbb{E}[Z_n] = \frac{\mathbb{E}[S_n]}{s_n} = 0.
  \]
  \item For \(\mathcal{N}(0, 1)\), \( \mathbb{E}[\mathcal{N}] = 0 \).
\end{itemize}
Therefore:
  \[
  f'(0) (\mathbb{E}[Z_n] - \mathbb{E}[\mathcal{N}]) = 0.
  \]

(b) $\boldsymbol{\frac{f''(0)}{2} (\mathbb{E}[Z_n^2] - \mathbb{E}[\mathcal{N}^2])}$
\begin{itemize}
    \item The variance of \( S_n \) is \( s_n^2 = \sum_{j=1}^n \sigma_j^2 \), so:
  \[
  \text{Var}(Z_n) = \frac{\text{Var}(S_n)}{s_n^2} = \frac{s_n^2}{s_n^2} = 1.
  \]
    \item Thus:
  \[
  \mathbb{E}[Z_n^2] = 1.
  \]
    \item For \( \mathcal{N}(0,1) \), \( \mathbb{E}[\mathcal{N}^2] = 1 \).
\end{itemize}
Therefore:
  \[
  \frac{f''(0)}{2} (\mathbb{E}[Z_n^2] - \mathbb{E}[\mathcal{N}^2]) = 0.
  \]

(c) $\boldsymbol{\mathbb{E}[R(Z_n)] - \mathbb{E}[R(\mathcal{N})]}$

By Taylor's theorem, We have:
\[
\mathbb{E}[R(Z_n)] \leq \frac{M}{6} \mathbb{E}[Z_n^3], 
\]
and

\[
\mathbb{E}[R(\mathcal{N})] \leq \frac{M}{6} \mathbb{E}[\mathcal{N}^3]
\]

where \( M = \sup_{x \in \mathbb{R}} |f^{(3)}(x)| \) is the maximum bound on the third derivative of \( f \).

Thus, 
\begin{equation}{\label{final_eq}}
    \left| \mathbb{E}[R(Z_n)] - \mathbb{E}[R(\mathcal{N})] \right| \leq \frac{M}{6} \left|\mathbb{E}[Z_n^3] - \mathbb{E}[\mathcal{N}^3] \right| 
\end{equation}

\textbf{For} $\boldsymbol{Z_n}$:

The normalized third moment of \( Z_n = S_n / s_n \) is:
\begin{equation}{\label{Z_cube}}
    \mathbb{E}[Z_n^3] = \frac{\mathbb{E}[|S_n|^3]}{s_n^3}.
\end{equation}

Using Triangle inequality for sums, which states:
\begin{equation}{\label{lya_Z}}
    \mathbb{E}[|S_n|^3] = \mathbb{E}\left[\left| \sum_{j=1}^n X_j \right|^3\right] \leq \sum_{j=1}^n \mathbb{E}[|X_j|^3],
\end{equation}

Combining \eqref{Z_cube} and \eqref{lya_Z} we get:
\[
\mathbb{E}[|Z_n|^3] \leq \frac{\sum_{j=1}^n \gamma_j}{s_n^3},
\]
where \( \gamma_j = \mathbb{E}[|X_j|^3] \).

Thus:
\[
\mathbb{E}[R(Z_n)] \leq \frac{M}{6} \frac{\sum_{j=1}^n \gamma_j}{s_n^3}.
\]

\textbf{For} $\boldsymbol{\mathcal{N}(0,1)}$:
The third moment of \( \mathcal{N} \) is constant:
\begin{equation}{\label{third_moment}}
    \mathbb{E}[\mathcal{N}^3] = 0,
\end{equation}

To prove \eqref{third_moment}, we use moment generating function (MGF). The moment generating function (MGF) of a random variable \( X \) is defined as:
\[
M_X(t) = \mathbb{E}[e^{tX}].
\]

For \( X \sim N(0, 1) \), the MGF is known to be:
\[
M_X(t) = e^{t^2 / 2}.
\]
This follows from integrating the product of \( e^{tx} \) and the PDF of \( N(0, 1) \):
\[
M_X(t) = \int_{-\infty}^\infty e^{tx} \frac{1}{\sqrt{2\pi}} e^{-x^2 / 2} \, dx = e^{t^2 / 2}.
\]

Then, third derivative:
   \[
   M_X^{(3)}(t) = \frac{d}{dt} \left( e^{t^2 / 2} + t^2 e^{t^2 / 2} \right).
   \]
   Differentiate term by term:
   \[
   M_X^{(3)}(t) = t^3 e^{t^2 / 2} + 3t e^{t^2 / 2}.
   \]
Now evaluate \( M_X^{(3)}(t) \) at \( t = 0 \):
\[
M_X^{(3)}(0) = (0^3 + 3 \cdot 0) e^{0} = 0.
\]

Thus:
\[
\mathbb{E}[X^3] = M_X^{(3)}(0) = 0.
\]

Hence, the difference simplifies to:
\[
\left| \mathbb{E}[Z_n^3] - \mathbb{E}[N^3] \right| = \left| \mathbb{E}[Z_n^3] \right| \leq \frac{\sum_{j=1}^n \gamma_j}{s_n^3} = \frac{\Gamma_n}{s_n^3}.
\]

Since \( \mathbb{E}[\mathcal{N}^3] = 0 \), the \eqref{final_eq} simplifies to:
\[
\left| \mathbb{E}[R(Z_n)] - \mathbb{E}[R(\mathcal{N})] \right| \leq \frac{M}{6} \mathbb{E}[Z_n^3].
\]

Substituting \( \mathbb{E}[Z_n^3] \leq \frac{\Gamma_n}{s_n^3} \), we get:
\[
\mathbb{E}[R(Z_n)] \leq \frac{M}{6} \frac{\Gamma_n}{s_n^3}.
\]

Finally, by the assumption:
\[
\frac{\Gamma_n}{s_n^3} \to 0 \quad \text{as } n \to \infty,
\]
it follows that:
\[
\mathbb{E}[f(Z_n)] \to \mathbb{E}[f(\mathcal{N})].

   \newpage

\subsubsection{Informal Proof}
Informal proof of Lyapounov's theorem for a single sequence by the method of Lindeberg \cite{chung2000course}.
\begin{itemize}
    \item \textbf{Notation and Statement}
    \begin{enumerate}
    \item \( \{X_j\}_{j=1}^n \) be a sequence of independent random variables with:
    \begin{itemize}
        \item[] \( \mathbb{E}[X_j] = 0 \), 
        \item[] \( \text{Var}(X_j) = \sigma_j^2 \) (finite variances, \( \sigma_j^2 < \infty \)),
        \item[] \( \mathbb{E}[|X_j|^3] = \gamma_j \) (finite third moments, \( \gamma_j < \infty \)).
    \end{itemize}
